<!-- R Commander Markdown Template -->

PRACTICA 5, DISTRIBUSIONES
=======================

### Your Name

### `r as.character(Sys.Date())`

```{r echo=FALSE}
# include this code chunk as-is to set options
knitr::opts_chunk$set(comment=NA, prompt=TRUE, out.width=750, fig.height=8, fig.width=8)
library(Rcmdr)
library(car)
library(RcmdrMisc)
```

2.Binomial

A multiple choice exam consists of 21 questions, each of which has 4 possible answers.
If a student answers all the questions at random,

a) Determine the distribution of the number of questions answered correctly by the
student.

X:Number of questions answered correctly by the student
X~B(21,0.25)

b) Represent the probability and distribution functions of this variable.

Binomial-function distribution y eso

c) Find the probability that the student just answers correctly to 6 questions. (Ans:
0.1770398).

Binomial-probabilidades binomial, y poner 21 y 0.25, luego buscar el 6

d) Find the probability of passing the exam if it is necessary to answer correctly to at
least 11 questions. (Ans: 0.00642271).

P(X>11)=1-P(X<=11)
Probabilidades Acumuladas hay q darle, valores d la variable, poner 10, y cola derecha xq es P(X>10) para incluir el 11


3.Poisson

The number of accesses per minute to a web site follows a Poisson distribution of
mean 5.


a) Represent the probability and distribution functions of this variable.

Menu, poisson, y meter los valores
X:number of accesses per minute
X~P(5)

b) Find the probability that, in one minute, exactly 4 accesses occur. (Ans: 0.1754673698).

Probabilidad de poisson, media 5, y buscar el 4

c) Find the probability that, in two minutes, the number of accesses will be, at most,
7. (Ans: 0.2202206).

como es el doble, es decir, una poisson mas la otra, porque son 2 minutos, la media es 5, buscamos 
P(X<=7), un lower tail vaya.
Probabilidad acumulada, valores pones 7 y media 10 por lo ya dicho

d) Think about the number of accesses that, at most, will occur in the next minute.
Determine the lowest value that we must give as an answer if we want to be right
with a probability of no less than 0.9. (Ans: 8 accesses)

buscamos el valor tal que P(X<=cK)=0.9, 0.9 es el cuantil.
vamos a cuantiles, 0.9 en probabilidad y pa lante

4.Geometric and negative binomial distribution

Represent the probability function of a geometric distribution with parameter 0.25.
Remember the relationship between the definition for geometric distribution seen in
theory classes and the definition used by R.


Consider the multiple choice exam described in Section 5.2 (binomial distribution)
and assume again that the student answers randomly to all questions:


a) Find the probability that the student gives his first correct answer, in the fourth
question he answers. (Ans: 0.1054687500).

probabilidades, geometrica, 0.25 y sale, en este caso en el 3, que indica que es la ultima respuesta fallada antes de la correcta, que seria la cuarta

b) Find the probability that you will need to answer, at most, 6 questions until you
get a correct answer. (Ans: 0.8220215).

P(X<=6), pero el putisimo R toma 0 como primer valor, asi que habra que buscar para X=5, siempre un valor menos que el que piden

c) Find the probability that the student gives his third correct answer on the sixth
question he answers. (Ans: 0.0659179688).

Binomial negativa, vamos a probabilidades, y en donde pone exitos, ponemos la cantidad de fallos antes del suceso que necesitamos
como nos dice que son 6 preuguntas y hemos fallado 3, buscamos el valor 3

Note: Remember that, when using R, if X ? B?(r, p) then P(X = k), with k ?
{0, 1, 2, . . .}, is the probability that we have k failures before the r-th success.

5.Hipergeometrica


A batch of 20 electronic devices contains five defective devices. If 10 devices are chosen at random, what is the probability that 2 of the 10 devices are defective? (Ans:
0.34829721). Note: If X follows a hypergeometric distribution, R defines P(X = t) as the
probability of finding t white balls among all the balls chosen at random.


N1 es 5
N2 es 15
k es 10

```{r echo=FALSE}
# include this code chunk as-is to enable 3D graphs
library(rgl)
knitr::knit_hooks$set(webgl = hook_webgl)
```


```{r}
local({
  .x <- 0:12
  plotDistr(.x, dbinom(.x, size=21, prob=0.25), xlab="Number of Successes", 
  ylab="Probability Mass", 
  main="Binomial Distribution:  Binomial trials=21, Probability of success=0.25", 
  discrete=TRUE)
})
```

```{r}
local({
  .x <- 0:12
  plotDistr(.x, pbinom(.x, size=21, prob=0.25), xlab="Number of Successes",
  ylab="Cumulative Probability", 
  main="Binomial Distribution:  Binomial trials=21, Probability of success=0.25", 
  discrete=TRUE, cdf=TRUE)
})
```

```{r}
local({
  .Table <- data.frame(Probability=dbinom(0:21, size=21, prob=0.25))
  rownames(.Table) <- 0:21 
  print(.Table)
})
```


```{r}
qbinom(c(10), size=21, prob=0.25, lower.tail=TRUE)
```

```{r}
pbinom(c(10), size=21, prob=0.25, lower.tail=TRUE)
```

```{r}
pbinom(c(10), size=21, prob=0.25, lower.tail=FALSE)
```

```{r}
local({
  .x <- 0:14
  plotDistr(.x, dpois(.x, lambda=5), xlab="x", ylab="Probability Mass", 
  main="Poisson Distribution:  Mean=5", discrete=TRUE)
})
```

```{r}
local({
  .x <- 0:14
  plotDistr(.x, ppois(.x, lambda=5), xlab="x",ylab="Cumulative Probability", 
  main="Poisson Distribution:  Mean=5", discrete=TRUE, cdf=TRUE)
})
```

```{r}
local({
  .Table <- data.frame(Probability=dpois(0:14, lambda=5))
  rownames(.Table) <- 0:14 
  print(.Table)
})
```


```{r}
qpois(c(7), lambda=10, lower.tail=TRUE)
```

```{r}
qpois(c(7), lambda=10, lower.tail=FALSE)
```

```{r}
ppois(c(7), lambda=10, lower.tail=TRUE)
```

```{r}
qpois(c(0.9), lambda=5, lower.tail=TRUE)
```

```{r}
local({
  .x <- 0:26
  plotDistr(.x, dgeom(.x, prob=0.25), xlab="Number of Failures until Success", 
  ylab="Probability Mass", main="Geometric Distribution:  Probability of success=0.25", 
  discrete=TRUE)
})
```

```{r}
local({
  .Table <- data.frame(Probability=dgeom(0:26, prob=0.25))
  rownames(.Table) <- 0:26 
  print(.Table)
})
```


```{r}
pgeom(c(6), prob=0.25, lower.tail=TRUE)
```

```{r}
pgeom(c(5), prob=0.25, lower.tail=TRUE)
```


```{r}
local({
  .Table <- data.frame(Probability=dnbinom(0:40, size=3, prob=0.25))
  rownames(.Table) <- 0:40 
  print(.Table)
})
```

```{r}
local({
  .Table <- data.frame(Probability=dhyper(0:2, m=10, n=10, k=2))
  rownames(.Table) <- 0:2 
  print(.Table)
})
```

```{r}
local({
  .Table <- data.frame(Probability=dhyper(0:5, m=5, n=15, k=10))
  rownames(.Table) <- 0:5 
  print(.Table)
})
```

```{r}
options(encoding="utf-8")
```


