<!-- R Commander Markdown Template -->

PRACTICA 8,REGRESIONES (SOLO LINEALES, NO DIO TIEMPO A MAS)
=======================

### Your Name

### `r as.character(Sys.Date())`

```{r echo=FALSE}
# include this code chunk as-is to set options
knitr::opts_chunk$set(comment=NA, prompt=TRUE, out.width=750, fig.height=8, fig.width=8)
library(Rcmdr)
library(car)
library(RcmdrMisc)
```


```{r echo=FALSE}
# include this code chunk as-is to enable 3D graphs
library(rgl)
knitr::knit_hooks$set(webgl = hook_webgl)
```


```{r}
load("C:/Users/Airam/Downloads/RCars_EN (2).RData")
```
The regression model we have to study is:
accel = ?0 + ?1 · cylindr + ?2 · HP + ?3 · weight + ?4 · engine + ?

a) Find and explain the coefficient of determination.

accel=17.9285204-0.2567606cylindr-0.0869459HP+0.0091757Weight-0.0003232engine the numbers are the coefficientes for B0 B1 B2 B3 B4 in that order


b) Is there a linear relationship between the regressor variables and the dependent
one? What conclusion is obtained for a level of significance ? = 0.05?

only the hp and the weight have a relationship between the dependent variable and the regressors
this is, we can take 0 on B1 and B2, and our model will be like:
accel=B3*weight+B4*engine+E

c) Can any of the model coefficients be assumed null, for a significance of 0.05?
B1 and B2

d) Express the model after obtaining estimates of the coefficient. Find 95 % confidence
intervals for the model coefficients.

accel=-0.2567606*0-0.0003232*0-0.0869459*B3+0.0091757*B4

```{r}
Model_1 <- lm(accel~cylind+engine+HP+weight, data=RCars_en)
summary(Model_1)
```

```{r}
library(MASS, pos=25)
```


```{r}
Confint(Model_1, level=0.95)
```

```{r}
options(encoding="utf-8")
```


