<!-- R Commander Markdown Template -->

PRACTICA 6, DISTRIBUSIONES CONTINUAS
=======================

### Your Name

### `r as.character(Sys.Date())`

```{r echo=FALSE}
# include this code chunk as-is to set options
knitr::opts_chunk$set(comment=NA, prompt=TRUE, out.width=750, fig.height=8, fig.width=8)
library(Rcmdr)
library(car)
library(RcmdrMisc)
```

2.Exponencial y Gamma

The failure-free operation time of a computer follows a random variable with an exponential distribution of average 20 minutes.

X:number of time of failure-free a pc has before failing
X~Exp(1/3) 1/3 porque es en horas


a) Represent the density and distribution functions of this variable.

lo de siempre

b) Find the probability that the failure-free operating time is at least 22 minutes. (Ans:
0.3328711).

Divides 22 entre 60 para saber el valor que buscas, y en probabilidades de la exponencial, lo pones y metes el valor de la distribucion

c) Determine a period of time such that, with probability 0.99, we can say that the
computer will work without failures during that period. (Ans: 0.2010067 min.).

P(x=cK)=0.99
cogemos el lower tail xq es el valor que incluye al cuantil q buscamos, y la probabilidad es 0.99

d) Determine the probability that the time between four consecutive failures is less
than 60 minutes.(Ans: 0.5768099).
esta es mas jodida de razonar, como son 4 intentos podriamos decir, la suma de todos 
sigue una distribucion gamma de parametro 3 y tasa de escala 1/3, que seria 1/a, siendo a=3
Y=X1+X2+X3~G(3,1/3)
P(Y<1) porque usamos horas aqui

Note: If X ? G(a, p), the shape parameter is p and the scale parameter is 1/a.
```{r echo=FALSE}
# include this code chunk as-is to enable 3D graphs
library(rgl)
knitr::knit_hooks$set(webgl = hook_webgl)
```


```{r}
local({
  .x <- seq(0.002, 22.805, length.out=1000)  
  plotDistr(.x, dexp(.x, rate=0.3333), cdf=FALSE, xlab="x", ylab="Density", 
  main=paste("Exponential Distribution:  Rate=0.3333"))
})
```

```{r}
1/1/3
```


```{r}
local({
  .x <- seq(0, 2.534, length.out=1000)  
  plotDistr(.x, dexp(.x, rate=3), cdf=FALSE, xlab="x", ylab="Density", 
  main=paste("Exponential Distribution:  Rate=3"))
})
```

```{r}
local({
  .x <- seq(0, 2.534, length.out=1000)  
  plotDistr(.x, pexp(.x, rate=3), cdf=TRUE, xlab="x", ylab="Cumulative Probability", 
  main=paste("Exponential Distribution:  Rate=3"))
})
```

```{r}
22/60
```


```{r}
pexp(c(0.3666667), rate=3, lower.tail=FALSE)
```

```{r}
qexp(c(0.99), rate=3, lower.tail=FALSE)
```

```{r}
qexp(c(0.99), rate=3, lower.tail=TRUE)
```

```{r}
0.003350112*60
```


```{r}
pgamma(c(1), shape=3, scale=0.33333, lower.tail=TRUE)
```


3.Distribucion Normal

The juice content (in liters), which an automatic filling process puts into the bottles,
follows a normal distribution with mean 2 and standard deviation 0.1.


a) Represent the density and distribution functions of this variable.
Menu de siempre

b) Find the probability that a bottle chosen at random contains more than 1.9 liters
of juice. (Ans: 0.8413447).

P(X>1.9)=1-P(X<=1.9), sabiendo esto metes un lower tail para que te incluya el valor, y a 1 le restas ese valor

c) Find the probability that a bottle chosen at random contains between 1.95 and 2.1
liters of juice. (Ans: 0.5328072).

esto es como calcular el area por debajo de 1.95 y por debajo de 2.1, haces
P(X<1.95)-P(X<2.1), es calcular la dferencia entre ambas basicamente

d) The filling of a bottle will be considered defective if the amount of juice it contains
is less than a certain amount. Find out what this amount must be if you want
the filling of the bottles to be considered defective only in 5 % of the cases. (Ans:
1.835515)

P(X<cK)=0.05
con esto buscas el cuantil y a chuparla

```{r}
local({
  .x <- seq(1.671, 2.329, length.out=1000)  
  plotDistr(.x, dnorm(.x, mean=2, sd=0.1), cdf=FALSE, xlab="x", ylab="Density", 
  main=paste("Normal Distribution:  Mean=2, Standard deviation=0.1"))
})
```

```{r}
local({
  .x <- seq(1.671, 2.329, length.out=1000)  
  plotDistr(.x, pnorm(.x, mean=2, sd=0.1), cdf=TRUE, xlab="x", 
  ylab="Cumulative Probability", 
  main=paste("Normal Distribution:  Mean=2, Standard deviation=0.1"))
})
```

```{r}
pnorm(c(1.9), mean=2, sd=0.1, lower.tail=TRUE)
```

```{r}
1-0.1586553
```


```{r}
pnorm(c(2.1), mean=2, sd=0.1, lower.tail=TRUE)
```

```{r}
pnorm(c(1.9), mean=2, sd=0.1, lower.tail=FALSE)
```

```{r}
pnorm(c(1.9), mean=2, sd=0.1, lower.tail=TRUE)
```

```{r}
0.8413447-0.1586553
```


```{r}
pnorm(c(2.1), mean=2, sd=0.1, lower.tail=TRUE)
```

```{r}
pnorm(c(1.9), mean=2, sd=0.1, lower.tail=TRUE)
```


```{r}
0.8413447-0.1586553
```


```{r}
pnorm(c(1.95), mean=2, sd=0.1, lower.tail=TRUE)
```

```{r}
0.8413447-0.3085375
```


```{r}
qnorm(c(0.05), mean=2, sd=0.1, lower.tail=TRUE)
```

4.Teorema del limite central

Central Limit Theorem: If X1, . . . , Xn is a simple random sample for a random
variable X, with mean µ and finite variance ?
2
, then X ? N

µ, ?
2
n

.
It is a good approximation if n ? 30.
For example, if X1, . . . , X40 is a s.r.s. for X ? U(0, 2), then
X =
X1 + · · · + X40
40
? N

1,
1
120
Let us experimentally verify this result. We will take a representative sample or X through menu Distributions ? Continuous distributions ? Uniform distribution
? Sample from uniform. Thus we get a dat set called TCL with 1000 rows ans 40 random values (columns) for a U(0, 2) distribution, simultaneously calculating the average
of each row. In the mean column of this data file we have a sample of size 1000 of the
variable X.
Now, through menu Graphs ? Density estimate represent the density function for
data mean.


```{r}
TCL <- as.data.frame(matrix(runif(1000*40, min=0, max=2), ncol=40))
rownames(TCL) <- paste("sample", 1:1000, sep="")
colnames(TCL) <- paste("obs", 1:40, sep="")
TCL <- within(TCL, {
  mean <- rowMeans(TCL[,1:40])
})
```

```{r}
densityPlot( ~ mean, data=TCL, bw=bw.SJ, adjust=1, kernel=dnorm, method="adaptive")
```

```{r}
curve(dnorm(x,mean=1,sd=1/sqrt(120)),add=TRUE,col="red")
```


```{r}
options(encoding="utf-8")
```


