<!-- R Commander Markdown Template -->

PRACTICA 7, TESTS DE NORMALIDAD
=======================

### Your Name

### `r as.character(Sys.Date())`

```{r echo=FALSE}
# include this code chunk as-is to set options
knitr::opts_chunk$set(comment=NA, prompt=TRUE, out.width=750, fig.height=8, fig.width=8)
library(Rcmdr)
library(car)
library(RcmdrMisc)
```


```{r echo=FALSE}
# include this code chunk as-is to enable 3D graphs
library(rgl)
knitr::knit_hooks$set(webgl = hook_webgl)
```


```{r}
load("C:/Users/Airam/Downloads/World95R.RData")
```


Usamos la comparacion de cuantiles y el saphiro wilk

ejemplo1
para el mundo95, estudiar normalidad de B_TO_D en OECD
alpha es 0.05
H0: X~(mu,var^2)
H1:X~/(mu,var^2)

```{r}
example1 <- subset(World95, subset=region=="OECD")
```


```{r}
normalityTest(~b_to_d, test="shapiro.test", data=example1)
```
We observe in the output that the p-value obtained is 0.0248. Since it is smaller than
the significance (? = 0.05), we reject the null hypothesis and say that this data are nor
normally distributed

```{r}
with(example1, qqPlot(b_to_d, dist="norm", id=list(method="y", n=1, 
  labels=rownames(example1))))
```

```{r}
normalityTest(~b_to_d, test="shapiro.test", data=example1)
```
We perform the Shapiro-Wilk test again and now obtain a p-value equal to 0.06335,
hence we do not reject the normality at ? = 0.05 significance, once we deleted case 49.


3.Confidence intervals and hypothesis tests for the mean of a normal population

X:quantity of tons of chemical product produced every day
Xhat=802+795+752+810+783/5=788.4

H0:mu=800
H1:mu=/800

como el p-valor es mayor a 0.05, quiere decir que no tenemos suficiente evidencia
a un nivel de confianza del 5% para rechazar H0
```{r}
802+795+752+810+783/5
```


```{r}
802+795+752+810+783
```


```{r}
3942/5
```

```{r}
load("C:/Users/Airam/AppData/Local/Temp/RtmpUtSjbB/Example2")
```

```{r}
with(Example2, (t.test(tons, alternative='less', mu=800, conf.level=.95)))
```

4.Confidence intervals and hypothesis tests for paired samples
X:time before
Y:time after
D:X-Y<0?
el p-valor es menor a 0.05, por lo que tenemos suficiente evidencia para rechazar la hipotesis H0
```{r}
load("C:/Users/Airam/AppData/Local/Temp/RtmpUtSjbB/Example4")
```


```{r}
with(Example4, (t.test(Time.bef, Time.aft, alternative='less', conf.level=.95, 
  paired=TRUE)))
```

5.Confidence Intervals and Hypothesis tests for a difference in two population means of two normal
independent populations

X:mean of treatment
Y:mean of placebo

H0:X-Y=0
H1:X-Y=/0

Para este, poner bien el conjunto de datos, y luego ir al test de medias independientes, y hacer el test que toca, que te lo da el propio menu

```{r}
load("C:/Users/Airam/AppData/Local/Temp/RtmpUtSjbB/Example5")
```


```{r}
options(encoding="utf-8")
```


